---
title: "Preliminary behavioral data"
author: "Wanjia Guo"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
library(gt)
library(fs)
library(purrr)
library(tidyverse)
theme_set(theme_minimal(18))
```


```{r setup, include=FALSE}

converting_read <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub))
}

converting_read2 <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub),
                                 resp_obj = as.character(resp_obj))
}

# Loading behavioral data
sub_dir = dir_ls(here::here("./csv_files/behavior"))
prescan_behav <- map(sub_dir, dir_ls, glob = '*prescan*_behav*.csv') %>% unlist()
scan_behav <- map(sub_dir, dir_ls, regexp = '(.*)_scan(\\d?\\d)_behav_.*') %>% unlist()
postscan1_behav <- map(sub_dir, dir_ls, glob = '*postscan1*_behav*.csv') %>% unlist()
postscan2_behav <- map(sub_dir, dir_ls, glob = '*postscan2*_behav*.csv') %>% unlist()

prescan_batch <- map_dfr(prescan_behav, converting_read)
scan_batch <- map_dfr(scan_behav, converting_read2)
postscan1_batch <- map_dfr(postscan1_behav, converting_read)
postscan2_batch <- map_dfr(postscan2_behav, converting_read)

```


## Total n = `r nrow(prescan_batch)/24`

Exclude subject 14: squzzed emergency ball while in the scanner.

```{r}
prescan_batch <- prescan_batch %>% filter(sub != 14)
scan_batch <- scan_batch %>% filter(sub != 14)
postscan1_batch <- postscan1_batch %>% filter(sub != 13 & sub != 14)
postscan2_batch <- postscan2_batch %>% filter(sub != 13 & sub != 14)
```

## n = `r nrow(prescan_batch)/24`

# QA

```{r}
scan_batch = scan_batch %>% 
  mutate(
  correct = ifelse(!is.na(resp_obj) & resp_obj == destination, 1, 0),
  confidence = ifelse(!is.na(conf_resp) & conf_resp == 6, 1, 0),
  cor_conf = ifelse(!is.na(resp_obj) & !is.na(conf_resp) & (resp_obj == destination & 
                       conf_resp== 6), 1, 0))
```

### Prescan

```{r}
prescan_batch = prescan_batch %>% 
  mutate(
  nquestion = rep(c(1, 2, 3), times = nrow(prescan_batch)/3),
  correct = ifelse(!is.na(resp_obj) & resp_obj == destination, 1, 0),
  confidence = ifelse(!is.na(conf_resp) & conf_resp == 6, 1, 0),
  cor_conf = ifelse((!is.na(resp_obj) & !is.na(conf_resp) &
                       resp_obj == destination & 
                       conf_resp== 6), 1, 0))

sub_plot = prescan_batch %>% 
  mutate(round_text = paste0('Round',round)) %>% 
  group_by(sub, nquestion, round_text, round) %>% 
  summarise(m = mean(correct), conf = mean(confidence),
            cor_conf = mean(cor_conf)) 

sub_plot %>% group_by(sub) %>% 
  summarise(correct = mean(m)) %>% 
  inner_join(
    sub_plot %>% group_by(sub) %>% 
    summarise(conf = mean(conf)) %>% 
    arrange(conf)) %>% 
  inner_join(
    sub_plot %>% group_by(sub) %>% 
    summarise(conf_correct = mean(cor_conf))) %>%
  gt() %>%
  fmt_number(
    columns = starts_with('co'),
    decimals = 3)%>%
  tab_header(title = "Prescan Performance") %>% 
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = vars(correct),
      rows = correct < 0.5
    )
  ) %>%
  tab_footnote(
    footnote = "accuracy < 0.5 are highlighted",
    locations = cells_column_labels(
      columns = vars(correct)
    )
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = vars(conf_correct),
      rows = conf_correct < 0.25
    )
  ) %>%
  tab_footnote(
    footnote = "confidence correct < 0.25 are highlighted",
    locations = cells_column_labels(
      columns = vars(conf_correct)
    )
  )
```

### Scan

```{r}
scan_batch %>% group_by(sub) %>% summarise(
  correct = mean(correct, na.rm = TRUE),
  conf = mean(confidence, na.rm = TRUE),
  conf_correct = mean(cor_conf, na.rm = TRUE)
) %>% gt() %>% 
  tab_header(title = "Scan Performance") %>% 
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = vars(correct),
      rows = correct < 0.5
    )
  )%>%
  tab_footnote(
    footnote = "accuracy < 0.5 are highlighted",
    locations = cells_column_labels(
      columns = vars(correct)
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = vars(conf_correct),
      rows = conf_correct < 0.25
    )
  ) %>%
  tab_footnote(
    footnote = "confidence correct < 0.25 are highlighted",
    locations = cells_column_labels(
      columns = vars(conf_correct)
    )
  )
```

### Posttest1

```{r}

postscan1_batch %>% 
  mutate(
  correct = ifelse(resp_obj == destination, 1, 0),
  conf = abs(resp)) %>% 
  group_by(sub, npic) %>% 
  summarise(m = mean(correct),
            conf = mean(conf)) %>% 
  gt() %>% 
  tab_header(title = "Postscan1 Performance",
             subtitle = "confidence range from 0 - 2.")

```

### Posttest2

```{r}
postscan2_batch = postscan2_batch %>% 
  mutate(
  correct = ifelse(!is.na(post_first_resp_obj) & post_first_resp_obj == destination, 1, 0))

postscan2_batch %>% group_by(sub) %>% 
  summarise(m = mean(correct)) %>% 
  gt() %>%
  tab_header(
    title = "Post scan 2 mean accuracy per subject"
  )%>% 
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = vars(m),
      rows = m < 0.5
    )
  )%>%
  tab_footnote(
    footnote = "accuracy < 0.5 are highlighted",
    locations = cells_column_labels(
      columns = vars(m)
    )
  )
```

# Prescan analysis

Participant were instructed to answer the expected destination for 3 times during the route: once at Same, once at Overlapping, and once at non-overlapping. They also indicated their confidence towards the choice (sure vs. unsure).

### Figures

```{r}
curr_plot = sub_plot %>%
  group_by(round_text, nquestion) %>% 
  summarise(mean = mean(m),
            se = sd(m)/sqrt(n()),
            mean_conf = mean(conf),
            conf_se = sd(conf)/sqrt(n()),
            mean_cor_conf = mean(cor_conf),
            cor_conf_se = sd(cor_conf)/sqrt(n()))


ggplot(curr_plot, aes(x = nquestion, y = mean)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Accuracy for pre-scan')
  
ggplot(curr_plot, aes(x = nquestion, y = mean_conf)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean_conf-conf_se, ymax=mean_conf+conf_se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Confidence response for pre-scan')
  #gt() %>% cols_align(align = 'left')

ggplot(curr_plot, aes(x = nquestion, y = mean_cor_conf)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean_cor_conf-cor_conf_se, ymax=mean_cor_conf+cor_conf_se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Confident correct for pre-scan')

sub_plot$round_text = factor(sub_plot$round_text)
```

```{r}

route_df <- data.frame(route=rep(c('pair1_east', 
                             'pair2_north', 
                             'pair3_west', 
                             'pair4_south'), each=2),
                 destination=c('bench', 'bikerack', 
                               'pole', 'window', 
                               'shrub', 'pergola', 
                               'entrance', 'map'),
                 competitor=c('bikerack','bench',
                               'window', 'pole', 
                               'pergola', 'shrub', 
                               'map', 'entrance'))

prescan_batch_competitor = prescan_batch %>% 
  inner_join(route_df, by = c('route', 'destination')) %>% 
  mutate(type = ifelse(resp_obj == destination, 'target',
                       ifelse(resp_obj == competitor, 'competitor',
                              'non-competitor')
                       ))
prescan_batch_competitor$type_no_na = prescan_batch_competitor$type %>% replace_na('non-competitor')
prescan_batch_competitor$type_no_na = factor(prescan_batch_competitor$type_no_na,
                                             levels = c('non-competitor',
                                                        'competitor',
                                                        'target'))

prescan_batch_competitor %>% 
  mutate(sub = as.factor(sub),
         nquestion = as.factor(nquestion),
         round = as.factor(round),
         type_no_na = as.factor(type_no_na)) %>% 
  count(sub, nquestion, round, type_no_na, .drop=FALSE) %>% 
  mutate(percentage = n / 4) %>% 
  group_by(nquestion, round, type_no_na) %>% 
  summarise(m = mean(percentage),
            se = sd(percentage)/sqrt(n()),
            n = n()) %>% 
  mutate(round_text = paste0('Round',round)) %>% 
  ggplot(aes(x = nquestion, y = m, fill = type_no_na)) + 
  geom_histogram(stat = "identity", position = 'dodge')+
  geom_errorbar(aes(ymin=m-se, ymax=m+se), color="black", width=0.1, size=0.5,
                position = position_dodge(0.9))+
  facet_wrap(~round_text)+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  labs(title = 'Correct for pre-scan,\nspearated by answer type',
       y = 'percentage',
       caption = '*non-competitor includes no response trials.'
       )+
  colorblindr::scale_fill_OkabeIto()
  
```

### Stats

ANVOA for Accuracy:

```{r}

sub_plot$nquestion = factor(sub_plot$nquestion)

ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = m
)
```

ANVOA for Confidence:

```{r}
ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = conf
)
```

ANVOA for high confidence accuracy:

```{r eval=FALSE, include=FALSE}
ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = cor_conf
)
```

t-test for mean (overlapping segment):

```{r eval=FALSE, include=FALSE}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$m,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$m,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$m,
       paired = TRUE)
```

t-test for confidence (overlapping segment):

```{r eval=FALSE, include=FALSE}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$conf,
       paired = TRUE)
```

t-test for high confidence accuracy (overlapping segment):

```{r eval=FALSE, include=FALSE}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$cor_conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$cor_conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$cor_conf,
       paired = TRUE)
```


# Scan analysis

Accuracy per round:

```{r eval=FALSE, include=FALSE}

scan_batch %>% mutate(pic_location = 
                            ifelse(npic < 50, 'early', 'late')) %>% 
  group_by(sub, pic_location) %>% 
  summarise(m = mean(correct))

scan_batch %>% mutate(pic_location = 
                            ifelse(npic < 50, 'early', 'late')) %>% 
  group_by(sub, pic_location) %>% 
  summarise(m = mean(cor_conf))

```


```{r}

curr_plot = scan_batch %>% group_by(round, sub) %>% summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)
) %>%
  group_by(round) %>% summarise(
  se_correct = sd(m_correct)/sqrt(n()),
  m_correct = mean(m_correct),
  se_conf_correct = sd(m_conf_correct)/sqrt(n()),
  m_conf_correct = mean(m_conf_correct)) %>% 
  pivot_longer(cols = starts_with('m_'),
                   names_to = 'type',
                   values_to = 'accuracy') %>% 
  pivot_longer(cols = starts_with('se_'),
                   names_to = 'se_type',
                   values_to = 'se') %>% 
  separate(type, c("A", "type", "C"), sep = '_') %>% 
  mutate(type = ifelse(type == 'conf', 'conf_correct', type)) %>% 
  select(-c(A, C)) %>% 
  separate(se_type, c("A", "se_type", "C"), sep = '_') %>% 
  mutate(se_type = ifelse(se_type == 'conf', 'conf_correct', se_type)) %>% 
  select(-c(A, C)) %>% 
  filter(type == se_type)

ggplot(curr_plot, aes(x = round, y = accuracy, color = type)) +
  geom_line(size = 1)+
  geom_errorbar(aes(ymin=accuracy-se, ymax=ifelse(accuracy+se>1, 1, accuracy+se)), width=0.1, size=0.5)+
  theme(legend.position = 'bottom')+
  labs('')+
  colorblindr::scale_color_OkabeIto()
```

Distribution of picture index:

Grouped in 10:

```{r fig.width=10, fig.height=12,eval=FALSE, include=FALSE}

curr_plot = scan_batch %>% 
  mutate(npic_10 = floor(npic/10)*10) %>% 
  group_by(npic_10, route, destination) %>% summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)) %>% 
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola',
                                   'pole','window','entrance','map')))

ggplot(curr_plot, aes(x = npic_10, y = m_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'Accuracy over picture')

ggplot(curr_plot, aes(x = npic_10, y = m_conf_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'High confidence accuracy over picture')

```


Grouped in 5:

```{r fig.width=10, fig.height=12, eval=FALSE, include=FALSE}

curr_plot = scan_batch %>% 
  mutate(npic_5 = floor(npic/5)*5) %>% 
  group_by(npic_5, route, destination) %>% summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)) %>% 
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola',
                                   'pole','window','entrance','map')))

ggplot(curr_plot, aes(x = npic_5, y = m_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'Accuracy over picture')

ggplot(curr_plot, aes(x = npic_5, y = m_conf_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'High confidence accuracy over picture')

```

Every picture:

```{r fig.width=10, fig.height=12, eval=FALSE, include=FALSE}

curr_plot = scan_batch %>% 
  group_by(npic, route, destination) %>% 
  summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)) %>% 
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola',
                                   'pole','window','entrance','map')))

ggplot(curr_plot, aes(x = npic, y = m_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'Accuracy over picture')

ggplot(curr_plot, aes(x = npic, y = m_conf_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'High confidence accuracy over picture')

```

# Posttest analysis

### Posttest 1

```{r}
postscan1_plot = postscan1_batch %>% 
  mutate(
  correct = ifelse(resp_obj == destination, 1, 0),
  conf = ifelse(correct == 1, abs(resp), 0)) %>%
  group_by(sub, npic) %>% 
  summarise(m = mean(correct),
            conf = mean(conf)) %>%
  group_by(npic) %>% 
  summarise(correct = mean(m),
            correct_se = sd(m)/sqrt(n()),
            confidence = mean(conf),
            conf_se = sd(conf)/sqrt(n()))

postscan1_plot$npic = factor(postscan1_plot$npic)

ggplot(postscan1_plot, aes(x = npic, y = correct)) + 
  geom_bar(stat = 'identity') + 
  geom_errorbar(aes(ymin = correct - correct_se, ymax = 
                      ifelse(correct + correct_se > 1, 1, correct + correct_se)
                      ),
                width = 0.2)

ggplot(postscan1_plot, aes(x = npic, y = confidence)) + 
  geom_bar(stat = 'identity') + 
  geom_errorbar(aes(ymin = confidence - conf_se, ymax = 
                      ifelse(confidence + conf_se > 2, 2, confidence + conf_se)
                      ),
                width = 0.2) + 
  labs(y = 'condidence correct') + 
  scale_y_continuous(
    breaks = c(0, 1, 2),
    labels = c("unsure/\nincorrect", "probably", "definitely"))
```

### Posttest 2

```{r}
avg = postscan2_batch %>% group_by(sub) %>% 
  summarise(m = mean(correct)) %>% 
  summarise(m = mean(m)) %>% .$m
```

Average accuracy = `r avg`

```{r fig.width=16, fig.height=10}
postscan2_batch %>%
  filter(correct == 1) %>%
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','shrub','pergola','pole','window','entrance','map'))) %>% 
  ggplot(aes(x = npic, fill = sub)) +
  geom_histogram() +
  geom_vline(xintercept=25) +
  geom_vline(xintercept=75) +
  labs(title = 'Picture index for correct trials')+
  facet_wrap(destination~route, ncol = 2)
```


```{r}
postscan2_batch %>% 
  filter(correct == 0 & resp != -999) %>%
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola','pole','window','entrance','map'))) %>% 
  ggplot(aes(x = npic, fill = sub)) +
  geom_histogram() +
  geom_vline(xintercept=25) +
  geom_vline(xintercept=75) +
  labs(title = 'Picture index for incorrect trials')+
  facet_wrap(destination~route, ncol = 2)
```


```{r}
postscan2_batch = postscan2_batch %>% mutate(tp = npic * 0.24, floor_tp = floor(tp), ceiling_tp = ceiling(tp))

postscan2_batch %>%
  filter(correct == 1) %>%
  ggplot(aes(x = ceiling_tp)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept=6) +
  geom_vline(xintercept=18) +
  labs(title = 'Timepoint for correct trials')+
  scale_x_continuous(breaks = seq(0,24,1))+
  xlab("Time (seconds)")+
  theme_classic()
```


```{r}
postscan2_batch %>%
  filter(correct == 1) %>%
  ggplot(aes(x = ceiling_tp)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept=6) +
  geom_vline(xintercept=18) +
  labs(title = 'Timepoint for correct trials')+
  scale_x_continuous(breaks = seq(0,24,1))+
  xlab("Time (seconds)")+
  theme_classic()
```

