---
title: "fMRI - separated timepoints"
author: "Wanjia Guo"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=16, fig.height=12) 

library(tidyverse)
library(fs)
library(ggplot2)
theme_set(theme_minimal(18))

library(ezPurrr)
library(ez)

cbPalette <- c("#CC79A7","#009E73","#0072B2","#E69F00","#56B4E9","#F0E442","#999999","#D55E00")
#pink, green, blue, yellow
```


```{r}

group_valid_type_phase = function(sample){
  
  sample = sample %>% mutate(phase = ifelse(round <= 5, 'early', 'late'))
  
  sample %>% group_by(valid, type, phase) %>% 
    summarise(m = mean(r) ,
              .groups = 'drop') %>% 
    pivot_wider(names_from = type,
                values_from = m)
}

calculate_mean = function(sample){
  
  summary = sample %>% 
    summarise(across_pair = mean(across_pair),
              within_pair = mean(within_pair),
              within_item = mean(within_item))
  
  summary
  
}
```

```{r reading in data}

re_process = FALSE
file_name =  './csv_files/R-tmp/all-sub-phase-df_n=20_1027.RDS'

if (re_process){
  
  rois_names = c('ca23dg-body', 'ppa','ca1-body','evc')
                 #'ca23dg', 'ca1',
                 #'angular_gyrus', 'evc', 
                 #'hippocampus', 'ppa')
  
  rdata_dir = here::here("./csv_files/cluster_RDS/")
  
  roi_dir = dir_ls(here::here("csv_files/cluster_RDS/"),  type = "directory")
  processed_sub_list = map(roi_dir, dir_ls) %>% unlist() %>% 
    map_chr(~gsub('.*/sub-([0-9]+)_.*','\\1', .x)) %>% 
    unlist() %>% 
    unique()
  
  remove('huge_df')
  
  for (roi in rois_names){
    for (sub in processed_sub_list){
      curr_df = readRDS(file.path(rdata_dir, roi, paste0('sub-', sub, '_', roi, '.RDS'))) %>% unnest(output) 
      
      curr_df$sub = sub
      curr_df$roi = roi
      if (exists('huge_df')){
        huge_df = rbind(huge_df, curr_df)
      } else(
        huge_df = curr_df
      )
    }
  }
  
  # Take long to run:
  all_sub_phase_df = huge_df %>% 
    broadcast(group_valid_type_phase)
  
  saveRDS(all_sub_phase_df, file = file_name)
  
  }else{
  all_sub_phase_df = readRDS(file = file_name)
}



```


```{r}
all_sub_phase_df = all_sub_phase_df %>% 
  filter(sub != '13' & sub != '14' & sub != '23' &
           sub != '20' & sub != '24' & sub != '27')
```

## n = `r length(unique(all_sub_phase_df$sub))`

# Early vs. Late

```{r}
all_sub_df_unnest = all_sub_phase_df %>% 
  select(-data) %>% unnest(output)

all_sub_df_clean = all_sub_df_unnest %>% 
  mutate(valid = ifelse(valid == 'invalid-valid',
                              'valid-invalid', valid))
```


```{r}
all_sub_phase_df_unnest = all_sub_phase_df %>% 
  unnest(output) %>% 
  select(-data) %>% 
  mutate(phase = ifelse(
    round1 <= 5, paste0('early-', phase),
    paste0('late-', phase)))

all_sub_phase_df_unnest = all_sub_phase_df_unnest %>% 
  mutate(valid = ifelse(valid == 'invalid-valid',
                              'valid-invalid', valid),
         phase = ifelse(phase == 'late-early',
                        'early-late', phase))

tmp = all_sub_phase_df_unnest %>% 
  filter(roi %in% c('ca23dg-body','ca1-body','ppa','evc')) %>% 
  #filter(phase %in% c('early-early', 'late-late')) %>% 
  mutate(wi_wp = within_item - within_pair,
                    wp_ap = within_pair - across_pair,
         segment = factor(segment, levels = c('same', 'overlapping', 'non-overlapping')))

  tmp$roi =  factor(tmp$roi,
                levels = c('ca23dg-body','ppa','ca1-body','evc'))
  
  tmp_sub = tmp %>% group_by(segment, valid, within_trial_TR, roi, phase) %>%
    summarise(wp_ap_m = mean(wp_ap),
              wp_ap_se = sd(wp_ap)/sqrt(n()),
              wi_wp_m = mean(wi_wp),
              wi_wp_se = sd(wi_wp)/sqrt(n()),
              )
  
  tmp_sub$roi =  factor(tmp_sub$roi,
                levels = c('ca23dg-body','ppa','ca1-body','evc'))
```

```{r}
tmp2 = tmp %>%
      group_by(sub, roi, segment, valid, phase) %>% 
      summarise(wp_ap_m = mean(wp_ap),
                wp_ap_se = sd(wp_ap)/sqrt(n()),
                wi_wp_m = mean(wi_wp),
                wi_wp_se = sd(wi_wp)/sqrt(n())
                )
  
  tmp2_mean = tmp2 %>% select(sub, roi, segment, valid, phase,
                              wp_ap_m,wi_wp_m) %>% 
    mutate(wp_ap = wp_ap_m, wi_wp = wi_wp_m) %>% 
    select(-c(wp_ap_m, wi_wp_m)) %>% 
    pivot_longer(cols = c(wp_ap, wi_wp),
                 names_to = 'type',
                 values_to = 'mean')
  
  tmp2_mean$phase = factor(tmp2_mean$phase,
                           levels = c("early-early",
                                      "late-late",
                                      "early-late"))
```

## Within_pair - Across_pair

```{r}
wp_ap =  tmp2_mean %>% 
      filter(type == 'wp_ap' & valid != 'invalid-invalid')

 wp_ap %>% 
      group_by(segment, roi, valid, type, phase) %>% 
      summarise(m = mean(mean),
                se = sd(mean)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = phase)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = wp_ap, aes(x = segment, y = mean, color = phase, group = phase), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_pair-across_pair')+ 
      theme( legend.position='bottom') + 
    facet_wrap(valid~roi,scales = 'free_y', ncol = 4)
```

### Zoom in figures


#### Early-early and late-late for ca23dg valid-valid

```{r}
fig_df =  wp_ap %>% filter(phase != 'early-late') %>% filter(roi == 'ca23dg-body' & valid == 'valid-valid')


fig_df %>% 
      group_by(segment, roi, valid, type, phase) %>% 
      summarise(m = mean(mean),
                se = sd(mean)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = phase)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = fig_df, aes(x = segment, y = mean, color = phase, group = phase), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_pair-across_pair')+ 
      theme( legend.position='bottom') + 
    facet_wrap(valid~roi,scales = 'free_y', ncol = 4)+
  colorblindr::scale_fill_OkabeIto()+ 
  colorblindr::scale_color_OkabeIto()
```

Segment x Phase Two-Way ANOVA

```{r}

d = fig_df

ezANOVA(data=d,
        wid=sub,
        within = .(segment, phase),
        dv = mean)$ANOVA %>% knitr::kable()
```

One-sample t-tests

```{r}

for (pha in unique(d$phase)){
  print(pha)
  for (seg in unique(d$segment)){
    print(seg)
    print(t.test(d %>% filter(segment == seg & phase == pha) %>% .$mean))
  }
}

```


Same vs. Overlapping for early-early correlation
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'early-early') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```

Same vs. Overlapping for late-late correlation
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'late-late') %>% .$mean,
       paired = TRUE)
```

Late-late vs. Early-early at same segment
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'same' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```

Late-late vs. Early-early at overlapping segment
```{r}
t.test(d %>% filter(segment == 'overlapping' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```


#### Early-early and late-late for ca23dg valid-invalid

```{r}
fig_df =  wp_ap %>% filter(phase != 'early-late') %>% filter(roi == 'ca23dg-body' & valid == 'valid-invalid')


fig_df %>% 
      group_by(segment, roi, valid, type, phase) %>% 
      summarise(m = mean(mean),
                se = sd(mean)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = phase)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = fig_df, aes(x = segment, y = mean, color = phase, group = phase), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_pair-across_pair')+ 
      theme( legend.position='bottom') + 
    facet_wrap(valid~roi,scales = 'free_y', ncol = 4)+
  colorblindr::scale_fill_OkabeIto()+ 
  colorblindr::scale_color_OkabeIto()
```

Segment x Phase Two-Way ANOVA

```{r}

d = fig_df

ezANOVA(data=d,
        wid=sub,
        within = .(segment, phase),
        dv = mean)$ANOVA %>% knitr::kable()
```

One-sample t-tests

```{r}

for (pha in unique(d$phase)){
  print(pha)
  for (seg in unique(d$segment)){
    print(seg)
    print(t.test(d %>% filter(segment == seg & phase == pha) %>% .$mean))
  }
}

```

Same vs. Overlapping for early-early correlation
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'early-early') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```

Same vs. Overlapping for late-late correlation
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'late-late') %>% .$mean,
       paired = TRUE)
```

Late-late vs. Early-early at same segment
```{r}
t.test(d %>% filter(segment == 'same' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'same' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```

Late-late vs. Early-early at overlapping segment
```{r}
t.test(d %>% filter(segment == 'overlapping' & phase == 'late-late') %>% .$mean,
       d %>% filter(segment == 'overlapping' & phase == 'early-early') %>% .$mean,
       paired = TRUE)
```


```{r 09/28 presentation tmp figures 5, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
valid = wp_ap %>% filter(phase != 'early-late') %>% filter(roi == 'ca23dg-body' & valid == 'valid-valid')

t.test(valid %>% 
         filter(segment == 'same' & phase == 'early-early') %>% .$mean)


t.test(fig_df %>% 
         filter(roi == 'ca23dg-body' & valid == 'valid-valid' & segment == 'overlapping' & phase == 'early-early') %>% .$mean)

t.test(fig_df %>% 
         filter(roi == 'ca23dg-body' & valid == 'valid-valid' & segment == 'non-overlapping' & phase == 'early-early') %>% .$mean)
```


```{r}
tmp_sub %>% 
  filter(roi != 'evc' & roi != 'ca1-body' & valid != 'invalid-invalid') %>% 
  ggplot(aes(x = within_trial_TR, y = wp_ap_m, color = roi)) +
    geom_vline(xintercept=6) +
    geom_vline(xintercept=18) +
    geom_ribbon(aes(ymin = wp_ap_m-wp_ap_se, 
                    ymax = wp_ap_m+wp_ap_se,
                    fill = roi),
                alpha = 0.2,
                color = NA) +
    geom_line(size = 1)+
    labs(y = 'within_pair - across_pair',
         x = 'within trial timepoint') + 
    theme(legend.position="bottom",
          legend.title = element_blank()) + 
      facet_wrap(valid~phase)+
    scale_fill_manual(values = cbPalette)+ 
    scale_color_manual(values = cbPalette)
  
```


```{r eval=FALSE, include=FALSE}

## Within_item - Within_pair

wi_wp =  tmp2_mean %>% 
      filter(type == 'wi_wp' & valid != 'invalid-invalid')

 wi_wp %>% 
      group_by(segment, roi, valid, type, phase) %>% 
      summarise(m = mean(mean),
                se = sd(mean)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = phase)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = wi_wp, aes(x = segment, y = mean, color = phase, group = phase), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_item-within_pair')+ 
      theme( legend.position='bottom') + 
    facet_wrap(valid~roi,scales = 'free_y', ncol = 4)
```

```{r eval=FALSE, include=FALSE}
tmp_sub %>% filter(roi != 'evc'& roi != 'ca1-body') %>% 
  ggplot(aes(x = within_trial_TR, y = wi_wp_m, color = roi)) +
    geom_vline(xintercept=6) +
    geom_vline(xintercept=18) +
    geom_ribbon(aes(ymin = wi_wp_m-wi_wp_se, 
                    ymax = wi_wp_m+wi_wp_se,
                    fill = roi),
                alpha = 0.2,
                color = NA) +
    geom_line(size = 1)+
    labs(y = 'within_item - within_pair',
         x = 'within trial timepoint') + 
    theme(legend.position="bottom",
          legend.title = element_blank()) + 
      facet_wrap(valid~phase)+
    scale_fill_manual(values = cbPalette)+ 
    scale_color_manual(values = cbPalette)
```



```{r 0522 presentation figures 1, eval=FALSE, include=FALSE}
tmp = df %>% mutate(wp_ap = within_pair - across_pair,
                      wi_wp = within_item - within_pair,
         segment = factor(segment, levels = c('same', 'overlapping', 'non-overlapping'))) %>% 
  filter(roi %in% c('ca23dg-body', 'ca1-body', 'ppa', 'evc')) %>% 
  filter(valid == 'invalid-invalid')

  tmp$roi =  factor(tmp$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))
  
  tmp_sub = tmp %>% group_by(segment, valid, within_trial_TR, roi) %>%
    summarise(wp_ap_m = mean(wp_ap),
              wp_ap_se = sd(wp_ap)/sqrt(n()),
              wi_wp_m = mean(wi_wp),
              wi_wp_se = sd(wi_wp)/sqrt(n()),
              )

  tmp_sub$roi =  factor(tmp_sub$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))

  tmp_sub %>% ggplot(aes(x = within_trial_TR, y = wp_ap_m, color = roi)) +
    geom_vline(xintercept=6) +
    geom_vline(xintercept=18) +
    geom_ribbon(aes(ymin = wp_ap_m-wp_ap_se, 
                    ymax = wp_ap_m+wp_ap_se,
                    fill = roi),
                alpha = 0.2,
                color = NA) +
    geom_line(size = 1)+
    labs(y = 'within_pair - across_pair',
         x = 'within trial timepoint') + 
    theme(legend.position="bottom",
          legend.title = element_blank())
  
  tmp2 = tmp %>%
      group_by(sub, roi, segment) %>% 
      summarise(wp_ap_m = mean(wp_ap),
                wp_ap_se = sd(wp_ap)/sqrt(n())
                )
  
  tmp3 = tmp2 %>%  group_by(segment, roi) %>% 
      summarise(m = mean(wp_ap_m),
                se = sd(wp_ap_m)/sqrt(n()),
                n = n())
  
  tmp2 %>% group_by(segment, roi) %>% 
      summarise(m = mean(wp_ap_m),
                se = sd(wp_ap_m)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = roi)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = tmp2, aes(x = segment, y = wp_ap_m, color = roi, group = roi), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_pair - across_pair')+ 
      theme( legend.position='none') + 
    facet_wrap(~roi,scales = 'free_y', ncol = 2)
```


```{r 0522 presentation figures 2, eval=FALSE, include=FALSE}
tmp = df %>% mutate(wi_wp = within_item - within_pair,
         segment = factor(segment, levels = c('same', 'overlapping', 'non-overlapping'))) %>% 
  filter(roi %in% c('ca23dg-body', 'ca1-body', 'ppa', 'evc')) %>% 
  filter(valid == 'valid-invalid')

  tmp$roi =  factor(tmp$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))
  
  tmp_sub = tmp %>% group_by(segment, valid, within_trial_TR, roi) %>%
    summarise(wi_wp_m = mean(wi_wp),
              wi_wp_se = sd(wi_wp)/sqrt(n()),
              )

  tmp_sub$roi =  factor(tmp_sub$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))

  tmp_sub %>% ggplot(aes(x = within_trial_TR, y = wi_wp_m, color = roi)) +
    geom_vline(xintercept=6) +
    geom_vline(xintercept=18) +
    geom_ribbon(aes(ymin = wi_wp_m-wi_wp_se, 
                    ymax = wi_wp_m+wi_wp_se,
                    fill = roi),
                alpha = 0.2,
                color = NA) +
    geom_line(size = 1)+
    labs(y = 'within_item - within_pair',
         x = 'within trial timepoint') + 
    theme(legend.position="bottom",
          legend.title = element_blank())
  
  tmp2 = tmp %>%
      group_by(sub, roi, segment) %>% 
      summarise(wi_wp_m = mean(wi_wp),
                wi_wp_se = sd(wi_wp)/sqrt(n())
                )
  
  tmp3 = tmp2 %>%  group_by(segment, roi) %>% 
      summarise(m = mean(wi_wp_m),
                se = sd(wi_wp_m)/sqrt(n()),
                n = n())
  
  tmp2 %>% group_by(segment, roi) %>% 
      summarise(m = mean(wi_wp_m),
                se = sd(wi_wp_m)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = roi)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = tmp2, aes(x = segment, y = wi_wp_m, color = roi, group = roi), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'within_item - within_pair')+ 
      theme( legend.position='none') + 
    facet_wrap(~roi,scales = 'free_y', ncol = 2)
```

```{r 0522 presentation figures 3, eval=FALSE, include=FALSE}

tmp = df %>% mutate(wi_wp = within_item - within_pair,
                    wp_ap = within_pair - across_pair,
         segment = factor(segment, levels = c('same', 'overlapping', 'non-overlapping'))) %>% 
  filter(roi == 'ca23dg-body')  %>% 
  filter(valid != 'invalid-invalid') 

  tmp$roi =  factor(tmp$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))
  
  tmp_sub = tmp %>% group_by(segment, valid, within_trial_TR, roi) %>%
    summarise(wp_ap_m = mean(wp_ap),
              wp_ap_se = sd(wp_ap)/sqrt(n()),
              wi_wp_m = mean(wi_wp),
              wi_wp_se = sd(wi_wp)/sqrt(n()),
              )

  tmp_sub$roi =  factor(tmp_sub$roi,
                levels = c('ca23dg-body','ca1-body','ppa','evc'))

  tmp2 = tmp %>%
      group_by(sub, roi, segment, valid) %>% 
      summarise(wp_ap_m = mean(wp_ap),
                wp_ap_se = sd(wp_ap)/sqrt(n()),
                wi_wp_m = mean(wi_wp),
                wi_wp_se = sd(wi_wp)/sqrt(n())
                )
  
  tmp2_mean = tmp2 %>% select(sub, roi, segment, valid, 
                              wp_ap_m,wi_wp_m) %>% 
    mutate(wp_ap = wp_ap_m, wi_wp = wi_wp_m) %>% 
    select(-c(wp_ap_m, wi_wp_m)) %>% 
    pivot_longer(cols = c(wp_ap, wi_wp),
                 names_to = 'type',
                 values_to = 'mean')
  
  tmp2_se = tmp2 %>% select(sub, roi, segment, valid, 
                              wp_ap_se,wi_wp_se) %>% 
    mutate(wp_ap = wp_ap_se, wi_wp = wi_wp_se) %>% 
    select(-c(wp_ap_se, wi_wp_se)) %>% 
    pivot_longer(cols = c(wp_ap, wi_wp),
                 names_to = 'type',
                 values_to = 'se')
  
  tmp2_new = full_join(tmp2_mean, tmp2_se)
  
  levels(tmp2_mean$type) <- c("S", "Ve", "Vi")
  
  tmp2_mean %>% group_by(segment, roi, valid, type) %>% 
      summarise(m = mean(mean),
                se = sd(mean)/sqrt(n()),
                n = n()
                ) %>% 
      ggplot(aes(x = segment, y = m, fill = valid)) +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = m-se, ymax = m+se), position = position_dodge(width = 0.9), width=0.5) +
      geom_point(data = tmp2_mean, aes(x = segment, y = mean, color = valid, group = valid), 
                  position=position_jitterdodge(
                    jitter.width = 0.2,
                    dodge.width = 0.9)) + 
      labs(y = 'similarities')+ 
      theme( legend.position='bottom') + 
    facet_wrap(~type,scales = 'free_y', ncol = 2)

```