---
title: "Segments analysis (with Python)"
author: "Wanjia Guo"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=10, fig.height=16) 

library(tidyverse)
library(fs)
library(ggplot2)
library(ez)
library(gt)
theme_set(theme_classic(12))

library(ezPurrr)

cbPalette <- c("#CC79A7","#009E73","#0072B2","#E69F00","#56B4E9","#F0E442","#999999","#D55E00")
#pink, green, blue, yellow
```

```{r reading in data, include=FALSE}
converting_read <- function(curr_path){
  print(curr_path)
  
  read_csv(curr_path) %>% mutate(sub = as.character(sub_x))
}

sub_dir = dir_ls(here::here("./csv_files/python_summary"))

rois_names = c('ca23dg-body', 'ca1-body', 
               'evc', 'ppa')

files <- map(sub_dir, dir_ls, glob = '*/*norolling_*summary_with_rounds.csv') %>% unlist()

norolling <- map_dfr(files, converting_read)
  
```

```{r together}
sub_p2 = norolling %>% 
  filter(valid != 'invalid-invalid') %>% 
  filter(sub != '13' & sub != '23') %>% 
  pivot_wider(names_from = type, values_from = cor) %>% 
  mutate(wp_ap = within - across) %>% 
  select(-c(across, within, same)) %>% 
  mutate('segment' = ifelse(within_trial_TR <= 6, 'same',
                            ifelse(within_trial_TR <= 18, 'similar','different')
                                   ),
         'time' = ifelse((round_x <= 5 & round_y <= 5), 'early',
                         ifelse((round_x > 5 & round_y > 5), 'late',
                                'others'))) %>%
  filter(time != 'others') %>% 
  group_by(valid, segment, roi, sub, time) %>% 
  summarise(m = mean(wp_ap),
            se = sd(wp_ap)/sqrt(n()),
            n = n())
p2 = sub_p2 %>% 
  group_by(valid, segment, roi, time) %>% 
  summarise(mean = mean(m),
            se = sd(m)/sqrt(n()),
            n = n())

p2$segment = factor(p2$segment, levels = c('same', 'similar', 'different'))
p2$roi = factor(p2$roi, levels = c('ca23dg-body', 'ppa', 'ca1-body', 'evc'))
p2$valid = factor(p2$valid, levels = c('valid-valid', 'valid-invalid', 'invalid-invalid'))

ggplot(p2, aes(x = segment, y = mean, fill = time)) +
      geom_hline(yintercept = 0, linetype="longdash") +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.8), width=0.5) +
      #geom_point(data = sub_p1, aes(x = segment, y = m, color = roi, group = roi), 
      #            position=position_jitterdodge(
      #              jitter.width = 0.2,
      #              dodge.width = 0.75)) + 
      labs(y = 'within_pair - across_pair')+ 
      facet_wrap(valid~roi, ncol = 2, scales = 'free_y')+
      theme(legend.position = 'none',
            legend.title = element_blank(),
            strip.background = element_blank())+ 
  scale_fill_manual(values = cbPalette)+ 
  scale_color_manual(values = cbPalette)

```

ANOVA across ROI (ca23dg & ppa), segment, valid, and time

```{r}
ezANOVA(data=sub_p2 %>% filter(roi %in% c('ca23dg-body', 'ppa')),
        wid=sub,
        within = .(valid, segment, roi, time),
        dv = m)$ANOVA %>% knitr::kable()
```

ANOVA across segment, valid, and time for PPA

```{r}
ezANOVA(data=sub_p2 %>% filter(roi == 'ppa'),
        wid=sub,
        within = .(valid, segment, time),
        dv = m)$ANOVA %>% knitr::kable()
```

ANOVA across segment, valid, and time for CA23DG

```{r}
ezANOVA(data=sub_p2 %>% filter(roi == 'ca23dg-body'),
        wid=sub,
        within = .(valid, segment, time),
        dv = m)$ANOVA %>% knitr::kable()
```

t-tests for early vs. late

```{r}

t = sub_p2 %>% 
  select(-c(se, n)) %>% 
  pivot_wider(names_from = time, values_from = m) %>% 
  group_by(valid, roi, segment) %>% 
  nest() %>% 
  broadcast(~t.test(.$early, .$late, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`early-late` = output) %>%
  select(-c(data, output)) %>% 
  pivot_wider(names_from = segment, values_from = `early-late`)

t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "valid"
  ) %>% 
  row_group_order(groups = c("valid-valid", "valid-invalid")) %>%
  tab_header(title = "Early vs. Late") %>% 
  fmt_number(
    columns = c(`same`, `similar`, `different`),
    decimals = 3
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `different`,
      rows = `different` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `same`,
      rows = `same` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `similar`,
      rows = `similar` < 0.05
    )
  ) 
```


t-tests for first half (early)

```{r}

t = sub_p2 %>% 
  filter(time == 'early') %>% 
  group_by(segment, valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$m)$p.value) %>% 
  unnest(output) %>% 
  #mutate(sig = ifelse(output <= 0.05, TRUE, FALSE)) %>% 
  select(-data) %>% 
  pivot_wider(names_from = valid,
              values_from = output)

a = sub_p2 %>% select(-c(se, n)) %>% 
  pivot_wider(names_from = valid,
              values_from = m) %>% 
  group_by(segment, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$`valid-valid`, .$`valid-invalid`, 
                    paired = TRUE)$p.value) %>%
  unnest(output) %>%
  mutate(paired = output) %>% 
  select(-c(data, output)) 

t = inner_join(t, a, by = c("segment", "roi"))

t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "segment"
  ) %>%
  row_group_order(groups = c("same","similar","different")) %>%
  tab_header(title = "Valid Stats") %>%
  
  fmt_number(
    columns = c(`valid-invalid`, `valid-valid`, paired),
    decimals = 3
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-invalid`,
      rows = `valid-invalid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-valid`,
      rows = `valid-valid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `paired`,
      rows = `paired` < 0.05
    )
  )
```

```{r}

t = sub_p2 %>% 
  filter(time == 'early') %>% 
  select(-c(se, n)) %>% 
  pivot_wider(names_from = segment, values_from = m) %>% 
  group_by(valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$same, .$similar, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`same-similar` = output) %>%
  broadcast(~t.test(.$similar, .$different, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`similar-different` = output) %>% 
  broadcast(~t.test(.$same, .$different, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`same-different` = output) %>% 
  select(-c(data, output))


t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "valid"
  ) %>%
  row_group_order(groups = c("valid-valid", "valid-invalid")) %>%
  tab_header(title = "Segment Stats") %>% 
  fmt_number(
    columns = c(`same-similar`, `similar-different`, `same-different`),
    decimals = 3
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `same-similar`,
      rows = `same-similar` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `similar-different`,
      rows = `similar-different` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `same-different`,
      rows = `same-different` < 0.05
    )
  ) 
```


t-tests for second half (late)

```{r}

t = sub_p2 %>% 
  filter(time == 'late') %>% 
  group_by(segment, valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$m)$p.value) %>% 
  unnest(output) %>% 
  #mutate(sig = ifelse(output <= 0.05, TRUE, FALSE)) %>% 
  select(-data) %>% 
  pivot_wider(names_from = valid,
              values_from = output)

a = sub_p2 %>% select(-c(se, n)) %>% 
  pivot_wider(names_from = valid,
              values_from = m) %>% 
  group_by(segment, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$`valid-valid`, .$`valid-invalid`, 
                    paired = TRUE)$p.value) %>%
  unnest(output) %>%
  mutate(paired = output) %>% 
  select(-c(data, output)) 

t = inner_join(t, a, by = c("segment", "roi"))

t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "segment"
  ) %>%
  row_group_order(groups = c("same","similar","different")) %>%
  tab_header(title = "Valid Stats") %>%
  
  fmt_number(
    columns = c(`valid-invalid`, `valid-valid`, paired),
    decimals = 3
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-invalid`,
      rows = `valid-invalid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-valid`,
      rows = `valid-valid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `paired`,
      rows = `paired` < 0.05
    )
  )
```



```{r}

t = sub_p2 %>% 
  filter(time == 'late') %>% 
  select(-c(se, n)) %>% 
  pivot_wider(names_from = segment, values_from = m) %>% 
  group_by(valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$same, .$similar, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`same-similar` = output) %>%
  broadcast(~t.test(.$similar, .$different, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`similar-different` = output) %>% 
  broadcast(~t.test(.$same, .$different, paired = TRUE)$p.value) %>% 
  unnest(output) %>% 
  mutate(`same-different` = output) %>% 
  select(-c(data, output))


t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "valid"
  ) %>%
  row_group_order(groups = c("valid-valid", "valid-invalid")) %>%
  tab_header(title = "Segment Stats") %>% 
  fmt_number(
    columns = c(`same-similar`, `similar-different`, `same-different`),
    decimals = 3
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `same-similar`,
      rows = `same-similar` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `similar-different`,
      rows = `similar-different` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `same-different`,
      rows = `same-different` < 0.05
    )
  ) 
```


```{r early and late}
sub_p1 = norolling %>% 
  filter(valid != 'invalid-invalid') %>% 
  filter(sub != '13' & sub != '23') %>% 
  pivot_wider(names_from = type, values_from = cor) %>% 
  mutate(wp_ap = within - across) %>% 
  select(-c(across, within, same)) %>% 
  mutate('segment' = ifelse(within_trial_TR <= 6, 'same',
                            ifelse(within_trial_TR <= 12, 'early-similar',
                                   ifelse(within_trial_TR <= 18, 'late-similar',
                                          'different')
                                   )),
         'time' = ifelse((round_x <= 5 & round_y <= 5), 'early',
                         ifelse((round_x > 5 & round_y > 5), 'late',
                                'others'))) %>% 
  filter(time != 'others') %>% 
  group_by(valid, segment, roi, sub, time) %>% 
  summarise(m = mean(wp_ap),
            se = sd(wp_ap)/sqrt(n()),
            n = n())

p1 = sub_p1 %>% 
  group_by(valid, segment, roi, time) %>% 
  summarise(mean = mean(m),
            se = sd(m)/sqrt(n()),
            n = n())

p1$segment = factor(p1$segment, levels = c('same', 'early-similar', 'late-similar', 'different'))
p1$roi = factor(p1$roi, levels = c('ca23dg-body', 'ppa', 'ca1-body', 'evc'))
p1$valid = factor(p1$valid, levels = c('valid-valid', 'valid-invalid', 'invalid-invalid'))
p1$time = factor(p1$time, levels = c('early', 'late'))

ggplot(p1, aes(x = segment, y = mean, fill = time)) +
      geom_hline(yintercept = 0, linetype="longdash") +
      geom_bar(stat = 'identity', alpha = 0.5, position = position_dodge()) + 
      geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.8), width=0.5) +
      #geom_point(data = sub_p1, aes(x = segment, y = m, color = roi, group = roi), 
      #            position=position_jitterdodge(
      #              jitter.width = 0.2,
      #              dodge.width = 0.75)) + 
      labs(y = 'within_pair - across_pair')+ 
      facet_wrap(valid~roi, ncol = 2, scales = 'free_y')+
      theme(legend.position = 'top',
            legend.title = element_blank(),
            strip.background = element_blank())+ 
  scale_fill_manual(values = cbPalette)+ 
  scale_color_manual(values = cbPalette)

```

ANOVA across ROI (ca23dg & ppa), segment, valid, and time

```{r}
ezANOVA(data=sub_p1 %>% filter(roi %in% c('ca23dg-body', 'ppa')),
        wid=sub,
        within = .(valid, segment, roi, time),
        dv = m)$ANOVA %>% knitr::kable()
```

ANOVA across segment and valid for PPA

```{r}
ezANOVA(data=sub_p1 %>% filter(roi == 'ppa'),
        wid=sub,
        within = .(valid, segment, time),
        dv = m)$ANOVA %>% knitr::kable()
```

ANOVA across segment and valid for CA23DG

```{r}
ezANOVA(data=sub_p1 %>% filter(roi == 'ca23dg-body'),
        wid=sub,
        within = .(valid, segment, time),
        dv = m)$ANOVA %>% knitr::kable()
```

t-tests for first half rounds (early)

```{r}
t = sub_p1 %>% 
  filter(time == 'early') %>% 
  group_by(segment, valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$m)$p.value) %>% 
  unnest(output) %>% 
  #mutate(sig = ifelse(output <= 0.05, TRUE, FALSE)) %>% 
  select(-data) %>% 
  pivot_wider(names_from = valid,
              values_from = output)

a = sub_p1 %>% select(-c(se, n)) %>% 
  pivot_wider(names_from = valid,
              values_from = m) %>% 
  group_by(segment, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$`valid-valid`, .$`valid-invalid`, 
                    paired = TRUE)$p.value) %>%
  unnest(output) %>%
  mutate(paired = output) %>% 
  select(-c(data, output)) 

t = inner_join(t, a, by = c("segment", "roi"))
t$segment = factor(t$segment, levels = c('same', 'early-similar', 'late-similar', 'different'))
t$roi = factor(t$roi, levels = c('ca23dg-body', 'ppa', 'ca1-body', 'evc'))


t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "segment"
  ) %>%
  row_group_order(groups = c("same","early-similar","late-similar","different")) %>%
  tab_header(title = "Valid Stats") %>%
  
  fmt_number(
    #columns = c(`valid-invalid`, `valid-valid`, `invalid-invalid`, paired),
    columns = c(`valid-invalid`, `valid-valid`, paired),
    decimals = 3
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-invalid`,
      rows = `valid-invalid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-valid`,
      rows = `valid-valid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `paired`,
      rows = `paired` < 0.05
    )
  )
```

t-tests for second half rounds (late)

```{r}
t = sub_p1 %>% 
  filter(time == 'late') %>% 
  group_by(segment, valid, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$m)$p.value) %>% 
  unnest(output) %>% 
  #mutate(sig = ifelse(output <= 0.05, TRUE, FALSE)) %>% 
  select(-data) %>% 
  pivot_wider(names_from = valid,
              values_from = output)

a = sub_p1 %>% select(-c(se, n)) %>% 
  pivot_wider(names_from = valid,
              values_from = m) %>% 
  group_by(segment, roi) %>% 
  nest() %>% 
  broadcast(~t.test(.$`valid-valid`, .$`valid-invalid`, 
                    paired = TRUE)$p.value) %>%
  unnest(output) %>%
  mutate(paired = output) %>% 
  select(-c(data, output)) 

t = inner_join(t, a, by = c("segment", "roi"))
t$segment = factor(t$segment, levels = c('same', 'early-similar', 'late-similar', 'different'))
t$roi = factor(t$roi, levels = c('ca23dg-body', 'ppa', 'ca1-body', 'evc'))


t %>% ungroup() %>% 
  gt(
    rowname_col = "row",
    groupname_col = "segment"
  ) %>%
  row_group_order(groups = c("same","early-similar","late-similar","different")) %>%
  tab_header(title = "Valid Stats") %>%
  
  fmt_number(
    #columns = c(`valid-invalid`, `valid-valid`, `invalid-invalid`, paired),
    columns = c(`valid-invalid`, `valid-valid`, paired),
    decimals = 3
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-invalid`,
      rows = `valid-invalid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `valid-valid`,
      rows = `valid-valid` < 0.05
    )
  )%>%
  tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold",
                color = "red")
      ),
    locations = cells_body(
      columns = `paired`,
      rows = `paired` < 0.05
    )
  )
```

